---
title: "ROC for OHI thresholds"
author: "Sean Anderson"
date: '2017-07-18'
output: html_document
---

Let's read in the data, source some functions, and manipulate the data so we can create some ROC curves at relevant thresholds for the OHI. The data we are working with is the cross validated (out-of-sample) simulation data. 

```{r}
setwd("analysis")
library(dplyr)
library(ggplot2)
source("0-ensemble-functions.R")

# bring in the simulated data and shape it for plotting:
clean_names <- dplyr::data_frame(
  method = c("CMSY", "COMSIR", "mPRM", "SSCOM",
    "gbm_ensemble", "rf_ensemble", "lm_ensemble", "mean_ensemble"),
  clean_method = c("CMSY", "COM-SIR", "mPRM", "SSCOM",
    "GBM Superensemble", "RF Superensemble", "LM Superensemble", "Mean Ensemble"),
  order = c(1, 2, 4, 3, 8, 7, 6, 5),
  label_fudge_x = c(
    0, -0.03,0,-0.04,
    0, 0,0,-0.05),
  label_fudge_y = c(
    0, -0.02,0.03,0.04,
    0, 0.02,0,-0.02))

d_sim <- readRDS("generated-data/cv_sim_long.rds")
d_sim <- suppressWarnings(inner_join(d_sim, clean_names))

get_performance <- function(validation_data) {
  d_sim_perf <- validation_data %>% group_by(test_iter, type, clean_method,
    order, label_fudge_x, label_fudge_y) %>%
    summarise(
      mare = median(abs(re)),
      mre = median(re),
      corr = cor(bbmsy_true_trans, bbmsy_est_trans, method = "spearman",
        use = "pairwise.complete.obs"))
  
  d_sim_perf$clean_method <- as.factor(d_sim_perf$clean_method)
  d_sim_perf$clean_method <- reorder(d_sim_perf$clean_method, d_sim_perf$order)
  
  d_sim_perf_slope <- filter(d_sim_perf, type == "slope")
  d_sim_perf <- filter(d_sim_perf, type == "mean")
  
  d_sim_perf_long <- reshape2::melt(d_sim_perf,
    id.vars = c("test_iter", "clean_method", "type", "order", 
      "label_fudge_x", "label_fudge_y"))
  d_sim_perf_summ <- d_sim_perf_long %>%
    group_by(clean_method, order, variable, label_fudge_x, label_fudge_y) %>%
    summarise(
      m = median(value),
      l = quantile(value, 0.25),
      u = quantile(value, 0.75)) %>%
    as.data.frame
  d_sim_perf_summ$text_col <- ifelse(grepl("ensemble", 
    d_sim_perf_summ$clean_method, ignore.case = TRUE),
    "grey20", "grey50")
  d_sim_perf_wide_temp <- reshape2::dcast(d_sim_perf_summ, 
    clean_method + order ~ variable,
    value.var = "m")
  d_sim_perf_wide_temp
}
d_sim_perf_wide <- get_performance(d_sim)
saveRDS(d_sim_perf_wide, "generated-data/d_sim_perf_wide.rds")

# Format basic simulation ensemble without covariates for plotting:
d_sim_basic <- readRDS("generated-data/cv_sim_mean_basic_long.rds")
d_sim_basic <- suppressWarnings(inner_join(d_sim_basic, clean_names))
d_sim_perf_wide_basic <- get_performance(d_sim_basic)
saveRDS(d_sim_perf_wide_basic, "generated-data/d_sim_perf_wide_basic.rds")
d_sim_basic$bbmsy_est[d_sim_basic$bbmsy_est > 10] <- NA
d_sim_basic <- na.omit(d_sim_basic)
```

Get ROC and AUC for models applied to simulation data with b/bmsy as the response. We'll test 3 threshold levels. 0.8, 1.45, and > 0.8 but < 1.45. The last one checks whether the model correctly put b/bmsy between 0.8 and 1.45 vs. above or below. 

```{r}
library("doParallel")
registerDoParallel(cores = parallel::detectCores())
.parallel <- ifelse(Sys.info()[["sysname"]] == "Windows", FALSE, TRUE)

d_sim_mean <- d_sim_basic %>% filter(type == "mean") %>%
  mutate(above_0.8 = ifelse(bbmsy_true > 0.8, 1, 0)) %>% 
  mutate(above_1.45 = ifelse(bbmsy_true > 1.45, 1, 0)) %>% 
  mutate(below_1.45_above_0.8 = ifelse(bbmsy_true < 1.45 & bbmsy_true > 0.8, 1, 0)) %>% 
  mutate(clean_method = paste(order, clean_method, sep = "-"))

d_sim_mean$Ensemble <- ifelse(grepl("ensemble", 
  d_sim_mean$clean_method, ignore.case = TRUE),
  "(a) Ensemble", "(b) Individual")

get_roc <- function(true, est) {
  library("pROC") # required or pROC:: will generate errors
  y <- pROC::roc(response = true, predictor = est)
  data.frame(sens = y$sensitivities, spec = y$specificities,
    auc = as.numeric(y$auc))
}

rocs_sim_mean_0.8 <- plyr::ddply(d_sim_mean, c("clean_method", "Ensemble"), 
  function(x) {
    get_roc(true = x$above_0.8, est = x$bbmsy_est)
  }, .parallel = .parallel)

rocs_sim_mean_1.45 <- plyr::ddply(d_sim_mean, c("clean_method", "Ensemble"), 
  function(x) {
    get_roc(true = x$above_1.45, est = x$bbmsy_est)
  }, .parallel = .parallel)

rocs_sim_mean_0.8_1.45 <- plyr::ddply(d_sim_mean, c("clean_method", "Ensemble"), 
  function(x) {
    get_roc(true = x$below_1.45_above_0.8, est = x$bbmsy_est)
  }, .parallel = .parallel)

saveRDS(rocs_sim_mean_0.8, file = "generated-data/rocs_sim_mean_0.8.rds")
saveRDS(rocs_sim_mean_1.45, file = "generated-data/rocs_sim_mean_1.45.rds")
saveRDS(rocs_sim_mean_0.8_1.45, file = "generated-data/rocs_sim_mean_0.8_1.45.rds")
```

Let's read in the model output and calculate the AUC values (area under the curve). 0.5 is as good as a coin flip. 1.00 is perfect.

```{r}
rocs_sim_mean_0.8 <- readRDS("generated-data/rocs_sim_mean_0.8.rds")
rocs_sim_mean_1.45 <- readRDS("generated-data/rocs_sim_mean_1.45.rds")
rocs_sim_mean_0.8_1.45 <- readRDS("generated-data/rocs_sim_mean_0.8_1.45.rds")

rocs_sim_mean_0.8 %>%
  group_by(clean_method) %>%
  summarise(auc = round(auc[1], 2)) %>% 
  arrange(-auc)

rocs_sim_mean_1.45 %>%
  group_by(clean_method) %>%
  summarise(auc = round(auc[1], 2)) %>% 
  arrange(-auc)

rocs_sim_mean_0.8_1.45 %>%
  group_by(clean_method) %>%
  summarise(auc = round(auc[1], 2)) %>% 
  arrange(-auc)
```

Now make the curves:

```{r}
make_roc_curves <- function(dat) {
  p <- ggplot(dat, aes(spec, sens, colour = clean_method, group = clean_method)) +
    geom_line() + coord_equal() +
    geom_abline(intercept = 1, slope = 1, lty = 2, col = "darkgrey") +
    xlim(1, 0) +
    xlab(expression(Rate~of~correctly~categorizing~B/B[MSY]~as < threshold)) +
    ylab(expression(Rate~of~correctly~categorizing~B/B[MSY]~as > threshold)) +
    theme_bw() +
    theme(plot.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank()) + facet_wrap(~Ensemble) +
    scale_colour_brewer(palette="Spectral", guide = guide_legend(title = "Model"))
  p
}
p <- make_roc_curves(rocs_sim_mean_0.8)
ggsave("../figs/ohi-roc-sim-0.8.png", width = 8, height = 5)

p <- make_roc_curves(rocs_sim_mean_1.45)
ggsave("../figs/ohi-roc-sim-1.45.png", width = 8, height = 5)

p <- make_roc_curves(rocs_sim_mean_0.8_1.45)
ggsave("../figs/ohi-roc-sim-0.8-1.45.png", width = 8, height = 5)
```
